\keyalignment{l} % Right-aligned entry keys

\begin{rubric}{Experience}
\entry*[September 2013 {---} \textit{Present}] 
\raggedleft\textbf{Statewide Vice President}\par Graduate Assistants United Bargaining Council \par \textit{United Faculty of Florida Executive Committee}
\text{\begin{itemize}[leftmargin=0.5in,itemindent=0,labelsep=0.25in]
		\item Facilitated graduate assistant bargaining council meetings, conference calls, and UFF Senate workshops.
		\item Oversaw bargaining council budget, and petitioned for renewed funding from UFF in 2014
		\item Led a series of breakout sessions on statewide organizing, graduate assistant fees, and GOTV at UFF Senate alongside UFF/FEA staff.
		\item Coordinated statewide effort to address exorbitant graduate assitant fees, resulting in multiple rallies, significant statewide press coverage, and a meeting with the SUSF Chancellor.
		\item Assisted University of Florida GAU in organizing and coordinating a rally to end fees, calling for a meeting the the Chancellor of State University System Board of Governors.
		\item Compiled statewide data on graduate assistant fees, and presented this infomations in a face-to-face meeting with the SUSF Chancellor.
\end{itemize}}\\[1ex]
\newpage
\entry*[April 2013 {---} \textit{Present}] 
\raggedleft\textbf{Co-President} \par \textit{UFF-USF Graduate Assistants United}
\text{\begin{itemize}[leftmargin=0.5in,itemindent=0,labelsep=0.25in]
		\item Organized a campaign for 100\% healthcare premium coverage, which was ultimately won in 2013 bargaining
		\item Designed and coordinated Fall 2013 membership drive, resulting in 115 new members
		\item Targeted strategic departments through ``Department Luncheons'' to recruit new representatives and activists, resulting in an increase from 3 to 11 department reps.
		\item Coordinated organizing workshop with FEA staff to activate and train new leaders at the beginning of Fall 2013
		\item Increased number of new student orientations attended from 3 in 2012 to 16 in 2014
		\item Actively engaged new leaders in organizing, bargaining, and grievance trainings. Recruited 3 leaders to attend a week-long intensive Summer Academy training with FEA.
		\item Forged closer ties with graduate student government, faculty union, staff union, and local AFL-CIO central labor council.
\end{itemize}}\\[1ex]
\entry*[September 2012 {---} May 2014] 
\raggedleft\textbf{Representative to USF Student Insurance Task Force} \par \textit{UFF-USF Graduate Assistants United}
\text{\begin{itemize}[leftmargin=0.5in,itemindent=0,labelsep=0.25in]
		\item Represented USF graduate assistants at Task Force meetings with administrators, who sought to reduce the cost and quality of the graduate assistant healthcare plan.
		\item Organized a ``Health Care Town Hall'' to confront administrators about significant increases in co-insurance, deductibles, and co-pays.
		\item Represented graduate assistants on statewide insurance consortium conference calls, maintaining the same level of benefits for GA's at USF while every other state consortium member experienced cutbacks.
\end{itemize}}\\[1ex]
\entry*[April 2012 {---} September 2012] 
\raggedleft\textbf{Web Committee Chair}\par \textit{UFF-USF Graduate Assistants United}
\text{\begin{itemize}[leftmargin=0.5in,itemindent=0,labelsep=0.25in]
		\item Developed new wordpress-based website and designed a custom theme from scratch.
		\item Contributed to development and maintenance of ``Office Visits'' website to track membership and office visits.
		\item Created a private cloud for easier dropbox-like sharing of resources between USF-GAU leaders.
\end{itemize}}\\[1ex]
\entry*[April 2012 {---} \textit{Present}] 
\raggedleft\textbf{UFF Senator} \par \textit{UFF-USF Graduate Assistants United}
\end{rubric}
\keyalignment{r} % Right-aligned entry keys
